\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{parskip}
\usepackage{xcolor}

\definecolor{heading}{HTML}{111111}
\definecolor{accent}{HTML}{444444}

% ---------- Section formatting ----------
\titleformat{\section}
{\large\bfseries\color{heading}}
{}{0pt}{}
\titlespacing*{\section}{0pt}{10pt}{6pt}

% ---------- Custom commands ----------
\newcommand{\resumeSubheading}[4]{
  \textbf{#1} \hfill #2\\
  \textit{#3} \hfill \textit{#4}\\[2pt] }

\newcommand{\resumeItem}[1]{\item #1}

\newenvironment{resumeBulletList}{
  \begin{itemize}[leftmargin=*,label={--}]
  }{
\end{itemize}
}

\begin{document}

% ---------- HEADER ----------
\begin{center} {
  \LARGE \textbf{Akash K}}\\[4pt]
  \href{https://akashktesla.com}{akashktesla.com} \;|\;
  \href{mailto:akashktesla@gmail.com}{akashktesla@gmail.com} \;|\;
  \href{https://github.com/akashktesla}{github} \;|\;
  +91-8838704695 \;|\;
  \href{https://www.linkedin.com/in/akashkolanchi}{akashkolanchi} \;|\;
\end{center}

% ---------- SUMMARY ----------
\section*{Summary}
Data Scientist with experience delivering end-to-end solutions across \textbf{machine learning, optimization, and data engineering}. Skilled in building predictive models, designing custom heuristics, and architecting AI-driven systems for logistics, retail, and healthcare domains. Strong background in \textbf{time series forecasting, statistical analysis, and scalable data pipelines}, with hands-on expertise in Python, cloud platforms (AWS, GCP), and modern ML frameworks. Recognized for innovation and problem-solving in high-impact projects.

% ---------- SKILLS ----------
\section*{Skills}
\textbf{Languages:} Python, SQL, Bash  \\
\textbf{ML:} scikit-learn, XGBoost, PyTorch \\
\textbf{Data:} Pandas, Spark, Snowflake, Teradata \\
\textbf{Cloud/DevOps:} AWS, SageMaker, Bedrock, GCP, Docker, Git \\
\textbf{Other:} Statistics, Visualization

% ---------- EXPERIENCE ----------
\section*{Experience}
\resumeSubheading
{Innova Solutions}{Hyderabad, IN}{Data Scientist}{Sep 2023 -- Present}

% ---------- PROJECTS ----------
\section*{Projects}

\resumeSubheading
{3D Bin Packing Optimization}{}{Gerdau}{}
\begin{resumeBulletList}
  \resumeItem{Solved a long-standing \textbf{3D bin packing problem} that had remained unsolved 
  for 2 years despite attempts with linear programming.}
  \resumeItem{Designed a custom heuristic using \textbf{First-Fit strategy combined with Genetic 
  Algorithms}, achieving near-optimal packing efficiency.}
  \resumeItem{Eliminated dependency on expensive third-party solvers and reduced logistics costs 
  significantly through improved container utilization.}
  \resumeItem{Leveraged \textbf{AWS SageMaker} for large-scale experimentation, training genetic 
  algorithms across multiple configurations in parallel to accelerate convergence.}
\end{resumeBulletList}

\resumeSubheading
{Delivery Date Prediction with Time Series Models}{}{Gerdau}{}
\begin{resumeBulletList}
  \resumeItem{Analyzed delivery dates manually entered by operators, identifying significant \textbf{white noise and inconsistencies} that reduced forecasting accuracy.}
  \resumeItem{Proposed a novel \textbf{heuristic standardization model} to generalize noisy inputs and establish a robust baseline.}
  \resumeItem{Designed a hybrid approach to \textbf{regress on residuals} from the heuristic model, improving predictive power and enabling more reliable scheduling.}
  \resumeItem{Developed, trained, and deployed time series models on \textbf{AWS SageMaker}, 
  leveraging scalable infrastructure for faster experimentation and reproducible workflows.}

\end{resumeBulletList}
\resumeSubheading
{Healthcare Data Migration}{}{Centene}{}
\begin{resumeBulletList}
  \resumeItem{Contributed to large-scale \textbf{data migration} following a company acquisition, integrating datasets across Snowflake and Teradata.}
  \resumeItem{Developed robust \textbf{Python ingestion pipelines} and automation scripts for data validation, transformation, and ETL workflows.}
  \resumeItem{Leveraged \textbf{AWS Glue} for orchestration and configured Snowflake + Teradata for accurate and secure data transfer.}
  \resumeItem{Implemented job scheduling and monitoring with \textbf{Control-M}, ensuring reliability and compliance in data workflows.}
\end{resumeBulletList}

\resumeSubheading
{Onboarding Automation}{}{McKesson}{}
\begin{resumeBulletList}
  \resumeItem{Designed and built an \textbf{AI-driven web automation extension} to automate complex onboarding workflows across internal web applications.}
  \resumeItem{Integrated an \textbf{MCP (Model Context Protocol) server} with a \textbf{Playwright-based automation layer}, enabling autonomous UI navigation and task execution.}
  \resumeItem{Developed a \textbf{custom bridge server} to securely translate AI decisions into deterministic browser actions.}
  \resumeItem{Implemented end-to-end workflow orchestration with validation, retries, and failure handling to ensure reliability in production environments.}
\end{resumeBulletList}

% ---------- EDUCATION ----------
\section*{Education}
\textbf{Amrita University}, B.Tech in Computer and Communication Engineering \hfill 2019 -- 2023\\
Relevant Coursework: Probability \& Statistics, ML, Data Mining, DBMS

% ---------- CERTIFICATIONS & AWARDS ----------
\section*{Certifications}
Google Cloud Professional Machine Learning Engineer \hfill 2025

\section*{Awards}
Innovation Award - Recognized for building automated ML pipeline adopted across teams

% ---------- FOOTER ----------
\vspace{6pt}
{\footnotesize References available upon request. \hfill Last updated: \today}

\end{document}
